Astr 513: Final Project

### 2016-05-08 Final_Project/ms.tex
Assocciated plots are now side by side

The correlation matrix is calculated from the covariance matrix according to
%
\begin{equation}
  \label{eq:correlation}
  Corr_{i,j} = \frac{\mathbf{C}_{i,j}}{\sqrt{\mathbf{C}_{i,i}}\sqrt{\mathbf{C}_{j,j}}}.
\end{equation}
%
Note that the correlation of a variable with itself is 1 by definition.
The correlation matrices for both of our data sets can be seen below in
figures \autoref{fig:cmatrix_betoule} and \autoref{fig:cmatrix_rest}.
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Betoule_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{betoule2014} sample. Overall very few correlations exist between
    samples, likely due to the averaging over redshift bins.}
  \label{fig:cmatrix_betoule}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.8\linewidth]{figures/Rest_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{rest2014} sample. Significant correlation exists between
    different samples due to dependencies on systematic variables
    as seen in \autoref{eq:RestCovMatrix}.}
  \label{fig:cmatrix_rest}
\end{figure}

@@

\subsection{Planck Priors}
\label{sec:planck_priors}
Our priors are given by the analysis of the \citet{planck2013} data set.
However, instead of simply using the posterior mean and variance of
the parameters from that analysis as priors in our project, we
employed the full \Planck likelihood as a prior. That is,
we first run the Code for Anisotropies in the Microwave Background (CAMB)
in order to obtain the temperature power spectrum $\mathcal{D}_l^{TT}$
and the polarization power spectrum $\mathcal{C}_l^{EE}$
and feed it into the \Planck likelihood code\footnote{More information
on the \Planck likelihood can be found here: 
\url{https://wiki.cosmos.esa.int/planckpla2015/index.php/CMB_spectrum_\%26_Likelihood_Code}.}.
The resulting likelihood
is our prior, and it captures any degeneracies in parameter space
observed by the \Planck analysis, as seen in \autoref{fig:planck_corner}. 
%
\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/corner_example.eps}
  \caption{Posterior distributions of the cosmological parameter
    analysis using just the \Planck likelihood. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:planck_corner}
\TM{THIS IS A PLACE HOLDER PLOT!} 
\end{figure}
%

@@

\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & 0      & 0 \\
    Betoule et al. (no priors) & 0      & 0 \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & 0      & 0 \\
    \end{tabular}
    \caption {\label{tab:lcdm}Posterior distirbutions of parameters in the
      $\Lambda$CDM model. uncertainties denote symmetrized 68\%
      confidence intervals maginalized over other parameters.
      \EW{Filler table for the lambda CDM fits}}
\end{table}
%
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \Planck likelihood only    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distirbutions of parameters in the
    wCDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals maginalized over other parameters.
    \EW{Just a filler for the table for the wCDM fits}}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data including the
    \Planck priors for a $w$CDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_prior_bestfit}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data without including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_noprior_corner}
\end{figure}
%
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data including the
    \Planck priors for a wCDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_withprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_lcdm_noprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data without including the
    \Planck priors for a $\Lambda$CDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_noprior_corner}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{figures/betoule_lcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data including the
    \Planck priors for a $\Lambda$CDM model. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_withprior_corner}
\end{figure}

>>>>

The correlation matrix is calculated from the covariance matrix according to
%
\begin{equation}
  \label{eq:correlation}
  Corr_{i,j} = \frac{\mathbf{C}_{i,j}}{\sqrt{\mathbf{C}_{i,i}}\sqrt{\mathbf{C}_{j,j}}}.
\end{equation}
%
Note that the correlation of a variable with itself is 1 by definition.
The correlation matrices for both of our data sets can be seen below in
\autoref{fig:cmatrix_both}.
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/Betoule_correlation.eps}
  \includegraphics[width=0.5\linewidth]{figures/Rest_correlation.eps}
  \caption{Correlation matrix of $\mu_0(z)$ from the
    \citet{betoule2014} sample on the left and \citet{rest2014} sample 
    on the right. Very few correlations exist in \citet{betoule2014} likely 
    due to the averaging over redshift bins. Significant correlation exists in 
    \citet{rest2014} due to dependencies on systematic variables
    as seen in \autoref{eq:RestCovMatrix}.}
%  \label{fig:cmatrix_betoule}
%\end{figure}
%
%\begin{figure}
%  \includegraphics[width=0.8\linewidth]{figures/Rest_correlation.eps}
%  \caption{Correlation matrix of $\mu_0(z)$ from the
%    \citet{rest2014} sample. Significant correlation exists between
%    different samples due to dependencies on systematic variables
%    as seen in \autoref{eq:RestCovMatrix}.}
  \label{fig:cmatrix_both}
\end{figure}

@@

\subsection{Planck Priors}
\label{sec:planck_priors}
Our priors are given by the analysis of the \citet{planck2013} data set.
However, instead of simply using the posterior mean and variance of
the parameters from that analysis as priors in our project, we
employed the full \Planck likelihood as a prior. That is,
we first run the Code for Anisotropies in the Microwave Background (CAMB)
in order to obtain the temperature power spectrum $\mathcal{D}_l^{TT}$
and the polarization power spectrum $\mathcal{C}_l^{EE}$
and feed it into the \Planck likelihood code\footnote{More information
on the \Planck likelihood can be found here: 
\url{https://wiki.cosmos.esa.int/planckpla2015/index.php/CMB_spectrum_\%26_Likelihood_Code}.}.
The resulting likelihood
is our prior, and it captures any degeneracies in parameter space
observed by the \Planck analysis, as seen in \autoref{fig:planck_corner}. 
%
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/corner_example.eps}
  \caption{Posterior distributions of the cosmological parameter
    analysis using just the \Planck likelihood. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:planck_corner}
\TM{THIS IS A PLACE HOLDER PLOT!} 
\end{figure}
%

@@

\begin{table}[h]
   \centering
    \begin{tabular}{l|cc}
    ~                          & $\Omega_m$ & $h$ \\ \hline
    Betoule et al.             & 0      & 0 \\
    Betoule et al. (no priors) & 0      & 0 \\
    Rest et al.                & 0      & 0 \\
    Rest et al. (no priors)    & 0      & 0 \\
    \end{tabular}
    \caption {\label{tab:lcdm}Posterior distributions of parameters in the
      $\Lambda$CDM model. Uncertainties denote symmetrized 68\%
      confidence intervals marginalized over other parameters.}
\end{table}
%
\begin{table}[h]
  \label{tab:wcdm}
  \centering
  \begin{tabular}{l|ccc}
    ~                          & $\Omega_m$ & $h$ & $w$ \\ \hline
    Betoule et al.             & 0                      & 0     & 0     \\
    Betoule et al. (no priors) & 0                      & 0     & 0     \\
    Rest et al.                & 0                      & 0     & 0     \\
    Rest et al. (no priors)    & 0                      & 0     & 0     \\
    \Planck likelihood only    & 0                      & 0     & 0     \\
  \end{tabular}
  \caption {Posterior distributions of parameters in the
    $w$CDM model for both data sets and the \Planck likelihood only. 
    Uncertainties denote symmetrized 68\%
    confidence intervals marginalized over other parameters.}
\end{table}
%
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_bestfit.eps}
  \caption{Best fit model of the \citet{betoule2014} data including the
    \Planck priors for a $w$CDM model. Blue points are the data with
    error bars corresponding to the diagonal of the provided covariance martrix.
    The solid black line is the most likely model from our MCMC chain.}
  \label{fig:betoule_wcdm_prior_bestfit}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/betoule_wcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data for a $w$CDM model. The left is without 
    \Planck priors and the right is with \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_wcdm_corner}
\end{figure}
%
\begin{figure}
  \includegraphics[width=0.5\linewidth]{figures/betoule_lcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/betoule_lcdm_withprior_corner.eps}
  \caption{Posterior distributions of the cosmological parameters in the
    analysis of the \citet{betoule2014} data for a $\Lambda$CDM model. The left is without 
    \Planck priors and the right is with \Planck priors. Contours denote the
    68\% and 95\% confidence projected areas; dashed lines in
    the 1D histograms refer to the 68\% confidence intervals.}
  \label{fig:betoule_lcdm_corner}
\end{figure}
%
